---
title: "CodeWars Kata Template"
output: html_document
---


# Challenge outline

Given two integers a and b, which can be positive or negative, find the sum of all the integers between and including them and return it. If the two numbers are equal return a or b.

Note: a and b are not ordered!
Examples (a, b) --> output (explanation)

```
(1, 0) --> 1 (1 + 0 = 1)
(1, 2) --> 3 (1 + 2 = 3)
(0, 1) --> 1 (0 + 1 = 1)
(1, 1) --> 1 (1 since both are same)
(-1, 0) --> -1 (-1 + 0 = -1)
(-1, 2) --> 2 (-1 + 0 + 1 + 2 = 2)
```


## My Final Function (accepted by CodeWars)

```{r}
get_sum <- function(a, b){
  sum(min(c(a,b)):max(c(a,b)))
}
```

## Sample tests

```{r, message=FALSE}
library(testthat)
test_that("Example", {
  expect_equal(get_sum(0, 1), 1)
  expect_equal(get_sum(0, -1), -1)
})

```


## Other Solutions I Liked

```{r, eval=FALSE}

get_sum <- function(a, b) {
  sum(a:b)
}

```

This solution is technically faster than mine and correct because R can use `:` to create a sequence in both the positive and negative directions. For example (-3):5 and 5:(-3) yield the same sequence of values. However, I believe the convention is to go low:high. So I appreciate this solution for its simplicity only, but would probably not recommend or use myself.



