---
title: "Descending Order"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Challenge outline

Your task is to make a function that can take any non-negative integer as an argument and return it with its digits in descending order. Essentially, rearrange the digits to create the highest possible number.

Examples:
Input: `42145` Output: `54421`

Input: `145263` Output: `654321`

Input: `123456789` Output: `987654321`


## My Attempts

```{r, eval=FALSE}

descending_order <- function(num){
  
  num_split <- as.numeric(unlist(strsplit(as.character(num), split = "")))
  for (i in 1:length(num)) {
    
  }
  
}

```

## My Final Function (accepted by CodeWars)

```{r}
descending_order <- function(num){
  
  as.numeric(
    paste(
      sort(
        as.numeric(
          unlist(strsplit(as.character(num), split = ""))),
        decreasing=T), 
      collapse="")
  )
  
}

```

This function works as expected, and was accepted. But the multiple class switches really irk me

## Sample tests

```{r, message=FALSE}
library(testthat)

test_that('Basic tests', {
  expect_equal(descending_order(0), 0)
  expect_equal(descending_order(15), 51)
  expect_equal(descending_order(123456789), 987654321)
})

```


## Other Solutions I Liked

```{r, eval=FALSE}

descending_order <- function(num){
  as.numeric(paste(sort(unlist(strsplit(toString(num), "")), decreasing = TRUE), collapse = ""))  
}

```

None of the other solutions were all that different from mine, but I appreciated learning about the `toString()` function from this example.


