---
title: "DNA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Challenge outline

Deoxyribonucleic acid (DNA) is a chemical found in the nucleus of cells and carries the "instructions" for the development and functioning of living organisms.

If you want to know more: http://en.wikipedia.org/wiki/DNA

In DNA strings, symbols "A" and "T" are complements of each other, as "C" and "G". You have function with one side of the DNA (string, except for Haskell); you need to get the other complementary side. DNA strand is never empty or there is no DNA at all (again, except for Haskell).

More similar exercise are found here: http://rosalind.info/problems/list-view/ (source)

Example: (input --> output)

```
"ATTGC" --> "TAACG"
"GTAT" --> "CATA"
```

```
dnaStrand []        `shouldBe` []
dnaStrand [A,T,G,C] `shouldBe` [T,A,C,G]
dnaStrand [G,T,A,T] `shouldBe` [C,A,T,A]
dnaStrand [A,A,A,A] `shouldBe` [T,T,T,T]
```

## My Attempts

```{r, eval=FALSE}

DNA_strand <- function(dna){

  complement <- {
    gsub("A", "T", dna)
    gsub("T", "A", dna)
    gsub("C", "G", dna)
    gsub("G", "C", dna)
  }

  output <- paste("String", dna, "is", complement)
  return(complement)

}

```


## My Final Function (accepted by CodeWars)

```{r}
DNA_strand <- function(dna){
  
  dna_vector <- unlist(strsplit(dna, "")) 
  
  for (i in 1:length(dna_vector)) {
    if (dna_vector[[i]] == "A") {
      dna_vector[[i]] <- "T"
    } else if (dna_vector[[i]] == "T") {
      dna_vector[[i]] <- "A"
    } else if (dna_vector[[i]] == "G") {
      dna_vector[[i]] <- "C"
    } else if (dna_vector[[i]] == "C") {
      dna_vector[[i]] <- "G"
    }
  }
  
  complement <- paste(dna_vector, collapse = "")
  
  return(complement)
  
}
```

## Sample tests

```{r, message=FALSE}
library(testthat)

test_that('Basic tests', {
  expect_equal(DNA_strand("AAAA"),"TTTT","String AAAA is")
  expect_equal(DNA_strand("ATTGC"),"TAACG","String ATTGC is")
  expect_equal(DNA_strand("GTAT"),"CATA","String GTAT is")
  expect_equal(DNA_strand("AAGG"),"TTCC", "String AAGG is")
  expect_equal(DNA_strand("CGCG"),"GCGC", "String CGCG is")
  expect_equal(DNA_strand("ATTGC"),"TAACG","String ATTGC is")
  expect_equal(DNA_strand("GTATCGATCGATCGATCGATTATATTTTCGACGAGATTTAAATATATATATATACGAGAGAATACAGATAGACAGATTA"),"CATAGCTAGCTAGCTAGCTAATATAAAAGCTGCTCTAAATTTATATATATATATGCTCTCTTATGTCTATCTGTCTAAT")
})

```


## Other Solutions I Liked

```{r, eval=FALSE}

DNA_strand <- function(dna){
  chartr("ACGT", "TGCA", dna)
}

```


The `chartr()` function is exactly what I was looking for at the beginning of this, but I wasn't able to find it! Looping over elements in my for loop was definitely less efficient coding wise and memory wise.


