---
title: "CodeWars Kata Template"
output: html_document
---


# Challenge outline

Check to see if a string has the same amount of 'x's and 'o's. The method must return a boolean and be case insensitive. The string can contain any char.

Examples input/output:

```
XO("ooxx") => true
XO("xooxx") => false
XO("ooxXm") => true
XO("zpzpzpp") => true // when no 'x' and 'o' is present should return true
XO("zzoo") => false
```



## My Final Function (accepted by CodeWars)

```{r}
xo <- function(s){
  split_string <- unlist(strsplit(toupper(s), ""))
  length(which(split_string == "X")) == length(which(split_string == "O"))
}
```

## Sample tests

```{r, message=FALSE}
library(testthat)

test_that("Sample Tests", {
  expect_equal(xo("xo"), TRUE)
  expect_equal(xo("xo0"), TRUE)
  expect_equal(xo("xxxoo"), FALSE)
})
```


## Other Solutions I Liked

```{r, eval=FALSE}

xo <- function(s){
  s <- unlist(strsplit(casefold(s), ""))
  sum(s == "o") == sum(s == "x")
}

```

This solution is a bit shorter code-wise when it comes to the comparison of the strings, but otherwise shares the same approach!
