---
title: "CodeWars Kata Template"
output: html_document
---


# Challenge outline

Some numbers have funny properties. For example:

```
89 --> 8¹ + 9² = 89 * 1

695 --> 6² + 9³ + 5⁴= 1390 = 695 * 2

46288 --> 4³ + 6⁴+ 2⁵ + 8⁶ + 8⁷ = 2360688 = 46288 * 51
```

Given a positive integer n written as abcd... (a, b, c, d... being digits) and a positive integer p

we want to find a positive integer k, if it exists, such as the sum of the digits of n taken to the successive powers of p is equal to k * n.
In other words:

`Is there an integer k such as : (a ^ p + b ^ (p+1) + c ^(p+2) + d ^ (p+3) + ...) = n * k`

If it is the case we will return k, if not return -1.

Note: n and p will always be given as strictly positive integers.


## My Final Function (accepted by CodeWars)

```{r}

digPow <- function(n, p) {
  
  n_vector <- as.numeric(unlist(strsplit(toString(n), "")))
  p_vector <- c(p, p + 1:length(n_vector))
  n_exp_p_vector <- c()
  
  for (i in 1:length(n_vector)) {
    n_exp_p_vector[i] <- n_vector[[i]]^p_vector[[i]]
  }

  if ((sum(n_exp_p_vector) %% n) == 0) {
    (sum(n_exp_p_vector) / n)
  } else {
    -1
  }
  
}

```

## Sample tests

```{r, message=FALSE}
library(testthat)

testing <- function(n, p, expect) {
  cat("n: ", n, " p: ", p, "\n")
  actual <- digPow(n, p)
  cat("actual:\n ", actual, "\n")
  cat("expect:\n ", expect, "\n")
  expect_equal(actual, expect)
}

test_that("fixed tests", {
  testing(89, 1, 1)
  testing(92, 1, -1)
  testing(46288, 3, 51)
  
})


```


## Other Solutions I Liked

```{r, eval=FALSE}


digPow <- function(n, p) {
  d <- as.integer(unlist(strsplit(as.character(n), "")))
  r <- sum(d^(seq(p, length.out = length(d)))) / n
  ifelse(r %% 1, -1, r)
}

```


This solution did a much better job making use of R's native vectorization (e.g. seq()) than I did with my for loop.

