---
title: "CodeWars Kata Template"
output: html_document
---


# Challenge outline

Simple, given a string of words, return the length of the shortest word(s).

String will never be empty and you do not need to account for different data types.


## My Final Function (accepted by CodeWars)

```{r}
find_short <- function(s){
  unlist(strsplit(s, " ")) %>%
    lapply(function(x) nchar(x)) %>%
    unlist() %>% min()
}
```

## Sample tests

```{r, message=FALSE}
library(testthat)

test_that("Example Tests", {
  expect_equal(find_short("bitcoin take over the world maybe who knows perhaps"), 3)
  expect_equal(find_short("turns out random test cases are easier than writing out basic ones"), 3)
  expect_equal(find_short("lets talk about javascript the best language"), 3)
  expect_equal(find_short("i want to travel the world writing code one day"), 1)
  expect_equal(find_short("Lets all go on holiday somewhere very cold"), 2)
  expect_equal(find_short("Let's travel abroad shall we"), 2)
})
```


## Other Solutions I Liked

```{r, eval=FALSE}
find_short <- function(s){
  min(nchar(unlist(strsplit(s, " "))))
}
```

I didn't realize nchar() would operate on each element of the vector string! Same general approach as my solution then, but efficient in not neeting an apply/map function.
