---
title: "CodeWars Kata Template"
output: html_document
---


# Challenge outline

Your task is to sort a given string. Each word in the string will contain a single number. This number is the position the word should have in the result.

Note: Numbers can be from 1 to 9. So 1 will be the first word (not 0).

If the input string is empty, return an empty string. The words in the input String will only contain valid consecutive numbers.

### Examples
```
"is2 Thi1s T4est 3a"  -->  "Thi1s is2 3a T4est"
"4of Fo1r pe6ople g3ood th5e the2"  -->  "Fo1r the2 g3ood 4of th5e pe6ople"
""  -->  ""
```


## My Attempts

```{r, eval=FALSE}

your_order <- function(sentence) {
  string <- sentence %>%
    strsplit(split = " ")
  
  index <- string %>%
    map(~str_remove_all(.x, "[[:alpha:]]") %>% as.numeric()) %>%
    unlist()
  
  string %>%
    unlist() %>%
    {.[index]} %>%
    paste(collapse = " ")
}
```

This function worked on the sample given, but this was just a coincidence that the indices matched. Upon submission, my function did not actually work, and I realized that my indexing was just wrong.

## My Final Function (accepted by CodeWars)

```{r}
library(purrr)
library(stringr)
your_order <- function(sentence) {
  string <- sentence %>% 
    strsplit(split = " ")
  
  index <- string %>%
    map(~str_remove_all(.x, "[[:alpha:]]") %>% as.numeric()) %>%
    unlist() 
  
  names(index) <- unlist(string)
  index %>%
    unlist() %>%
    sort() %>%
    names() %>%
    paste(collapse = " ")
}
```

## Sample tests

```{r, message=FALSE}
library(testthat)

test_that("Example Test", {
  expect_equal(your_order("is2 Thi1s T4est 3a"), "Thi1s is2 3a T4est")
})
```


## Other Solutions I Liked

```{r, eval=FALSE}

your_order <- function(s){
  l <- unlist(strsplit(s, " "))
  names(l) <- as.numeric(gsub("[[:alpha:]]", "", l))
  paste(l[order(names(l))], collapse = " ")
}

```

I think the solution above is, at minimum, a more concise implementation of essentially the same process I did, and avoided using any {tidyverse} functions.
